---
title: "Burden of Congenital toxoplasmosis"
author: "Salvator Minani"
date: "2024-10-01"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### SETTINGS
## set seed to allow for reproducibility
```{r}
set.seed(264)
```

## number of iterations
```{r}
n <- 1e5
```

### PARAMETER VALUES FOR DALY
## define population matrix
```{r}
pop_mx <-
  matrix(c(893872, 1486390, 2459411, 470882, 218877,
           888554, 1514133, 2568012, 481213, 234234),
         ncol = 2)
```

### Number of Live births
```{r}
Live_births <- 437685
```

### Stillbirths after gestational week 22
```{r}
Still_births<- 7505
```

### Number of reported spontaneous abortions occurring up to 22 weeks of gestation
```{r}
Abortion <- 11616
```

### Total number of pregnancies
```{r}
Tot_Preg <- Live_births+Still_births+Abortion
```

### Probability of seronegative pregnant women, Beta parameters
```{r}
Pseroneg_alpha <- 3132
Pseroneg_beta <- 4330-3132
Pseroneg <-rbeta(n, Pseroneg_alpha, Pseroneg_beta)
```

### Probability of pregnant women getting infected during pregnancy, Beta parameters
```{r}
Pserop_alpha <-30
Pserop_beta <-(3132-30)
Pserop<- rbeta(n,Pserop_alpha, Pserop_beta)
```

### Total number of seroconverting pregnant women
```{r}
Nseroconv <-Tot_Preg*Pseroneg*Pserop
```

### Probability of trans-placental transmission-Mother-foetus
```{r}
PTTMoth_fet <- 0.281
```

### Probability of fetal loss in sero-converting mothers, uniform parameters
```{r}
P_fetalloss_min <- 0.017
P_fetalloss_max <- 0.04
P_fetalloss <-runif(n, P_fetalloss_min,P_fetalloss_max)
```

### Number of foetal losses due to CT > 22 weeks of gestation
```{r}
Nfetalloss<-Nseroconv*P_fetalloss*((40-22)/40)
```

### Incidence congenital toxoplasmosis
```{r}
 Inc_CT <-3132*Pserop*PTTMoth_fet
```

### Incidence of congenital toxoplasmosis cases per 1000 births
```{r}
Inc_CT_bi <-Inc_CT*(1000/3132)
```

### Total number of postnatal with CT
```{r}
Cases_CT <- ((Inc_CT_bi * Live_births)/1000)
```

### Proportion of pregnant women not taking Toxo medicine 
```{r}
PNtreat_toxo <-0.97
```

### Total number of postnatal with CT without health care
```{r}
Cases_CT_NHC <- Cases_CT*PNtreat_toxo
```

### DURATION OF TOXO SEQUELAE
### Duration of toxo sequelae (life long, CNS, HYDRO, ICcalcification, chorioretinitis at birth)
```{r}
Duration_LE_Bi <-59.7
```

### Duration of chorioretinitis later in life
```{r}
Duration_later_Bi <-59.7-10
```

### Standard life expectancy-GBD 2019 for YLLs
```{r}
Duration_GBD <-88.87
```

### DISABILITY WEIGHTS
## Disability Weight for patients with chorioretinitis-early
```{r}
DW_chorio1<-0.089
```

## Disability Weight for patients with chorioretinitis-later
```{r}
DW_chorio2<-0.089
```

## Disability Weight for patients with hydrocephalus
```{r}
DW_Hydro<-0.36
```

## Disability Weight for patients with intracranial calcifications
```{r}
DW_ICC<-0.01
```

## Disability Weight for patients with CNS abnormalities
```{r}
DW_CNSab<-0.36
```

## Disability weight for neonatal death
```{r}
DW_Neon<-1
```

### Disability weight for foetal loss
```{r}
DW_Floss<-1
```

#### DALY ESTIMATION PARAMETERS (no hospitals, DW and duration)
### Proportion of neonates with chorioretinitis at birth, Beta parameters
```{r}
Chorio1_alpha<-141
Chorio1_beta<-1048-141
Chorio1<-rbeta(n, Chorio1_alpha,Chorio1_beta)
```

### Number of neonates with chorioretinitis at birth
```{r}
NT_Chorio1 <- Cases_CT_NHC*Chorio1
```

### YLD for untreated neonates with chorioretinitis at birth
```{r}
YLD_NT_Chorio1<-NT_Chorio1*Duration_LE_Bi*DW_chorio1
```

### Proportion of children with chorioretinitis later in life, fixed
```{r}
Chorio2<-0.16
```

### Number of children with chorioretinitis later in life
```{r}
NT_Chorio2 <- Cases_CT_NHC*Chorio2
```

### YLD for untreated children with chorioretinitis later in life
```{r}
YLD_NT_Chorio2 <-NT_Chorio2*Duration_later_Bi*DW_chorio2
```

### Proportion of neonates with hydrocephalus, beta parameters
```{r}
Hydroc_alpha<-16
Hydroc_beta<-856-16
Hydrocephalus <- rbeta(n, Hydroc_alpha, Hydroc_beta)
```

### Number of neonates with hydrocephalus
```{r}
 NT_hydrocephalus<-Cases_CT_NHC*Hydrocephalus
```

### YLD for untreated neonates with hydrocephalus
```{r}
YLD_NT_hydrocephalus<-NT_hydrocephalus*Duration_LE_Bi*DW_Hydro
```

### Proportion of neonates with intracranial calcifications, beta parameters
```{r}
IC_Calc_alpha<-88
IC_Calc_beta<-837-88
IC_Calcification <-rbeta(n, IC_Calc_alpha, IC_Calc_beta)
```

### Number of neonates with intracranial calcification
```{r}
NT_IC_calcification <-Cases_CT_NHC*IC_Calcification
```

### YLD for untreated neonates with intracranial calcification
```{r}
YLD_NT_ICC<-NT_IC_calcification*Duration_LE_Bi*DW_ICC
```

#### Proportion of neonates with CNS abnormalities, Beta parameters
```{r}
CNS_alpha<-3
CNS_beta<-105-3
CNS_ab <-rbeta(n, CNS_alpha, CNS_beta)
```
### Total number of neonates with CNS abnormalities
```{r}
NT_CNS_abnorm <-Cases_CT_NHC*CNS_ab
```

### YLD for untreated neonates with CNS abnormalities
```{r}
YLD_NT_CNS<-NT_CNS_abnorm*Duration_LE_Bi*DW_CNSab
```

### Proportion of neonates that die, Beta parameters
```{r}
Neon_die_alpha<-9
Neon_die_beta<-1211-9
Neon_deaths<-rbeta(n, Neon_die_alpha, Neon_die_beta)
```

### Number of neonatal deaths
```{r}
NT_Neon_deaths<-Cases_CT_NHC*Neon_deaths
```

### YLL for untreated neonatal deaths
```{r}
YLL_NT_neo_death<-NT_Neon_deaths*Duration_GBD*DW_Neon
```
### YLL for foetal loss during pregnancy
```{r}
YLL_floss<-Nfetalloss*Duration_GBD*DW_Floss
```

### DALY PARAMETERS (HOSPITAL VISITS)

### Proportion of pregnant women visiting major hospitals and treated
```{r}
PTreat_toxo <- 1-PNtreat_toxo
```

### Total number of postnatal with CT with treatment at  health care
```{r}
Cases_CT_treat_HC <- Cases_CT*PTreat_toxo
```

### Probability of treatment reducing congenital transmission, fixed 
```{r}
spiramycin_reduction <- 0.5
```

### Number of neonates with chorioretinitis from treated women 
```{r}
NTreat_Chorio1 <-Cases_CT_treat_HC*Chorio1*spiramycin_reduction
```

### YLL for neonates with chorioretinitis at birth from treated women
```{r}
YLD_Treat_chorio1<-NTreat_Chorio1*Duration_LE_Bi*DW_chorio1
```

### Number of neonates with chorioretinitis later in life from treated women
```{r}
 NTreat_Chorio2 <- Cases_CT_treat_HC*Chorio2*spiramycin_reduction
```

### YLD for neonates with chorioretinitis later in life from treated women
```{r}
YLD_Treat_chorio2 <-NTreat_Chorio2*Duration_later_Bi*DW_chorio2
```

### Number of neonates with hydrocephalus from women treated 
```{r}
NTreat_hydroc<-Cases_CT_treat_HC*Hydrocephalus*spiramycin_reduction
```

### YLD for neonates with hydrocephalus from women treated
```{r}
YLD_Treat_hydroc <-NTreat_hydroc*Duration_LE_Bi*DW_Hydro
```

### Number of neonates with intracranial calcification from treated women
```{r}
NTreat_IC_calc <-Cases_CT_treat_HC*IC_Calcification*spiramycin_reduction
```

### YLD for neonates with intracranial calcification from treated women
```{r}
YLD_Treat_ICC<-NTreat_IC_calc*Duration_LE_Bi*DW_ICC
```

### Number of neonates with CNS abnormalities from women treated 
```{r}
NTreat_CNS_ab <-Cases_CT_treat_HC*CNS_ab*spiramycin_reduction
```

### YLD for Number of neonates with CNS abnormalities from women treated
```{r}
YLD_Treat_CNS <-NTreat_CNS_ab*Duration_LE_Bi*DW_CNSab
```

#### Number of neonatal deaths from treated women
```{r}
NTreat_Neon_deaths<-Cases_CT_treat_HC*Neon_deaths*spiramycin_reduction
```

### YLL for neonatal deaths from treated women
```{r}
YLL_Treat_neo_death<-NTreat_Neon_deaths*Duration_GBD*DW_Neon
```

### DISABILITY ADJUSTED LIFE YEARS
## social weighting - select one of these
```{r}
K <- 0; r <- 0     # DALY[0;0]
#K <- 0; r <- 0.03  # DALY[0;0.03]
#K <- 1; r <- 0     # DALY[1;0]
#K <- 1; r <- 0.03  # DALY[1;0.03]
```

### Years Lived with Disability, Untreated cases
```{r}
YLD_NT_all <- YLD_NT_Chorio1+YLD_NT_Chorio2+YLD_NT_hydrocephalus+YLD_NT_ICC+YLD_NT_CNS
```

### Years Lived with Disability, treated cases
```{r}
YLD_Treat_all <-YLD_Treat_chorio1+YLD_Treat_chorio2+YLD_Treat_hydroc+YLD_Treat_ICC+YLD_Treat_CNS
```

## Years Lived with Disability, total
```{r}
YLD_all <- YLD_NT_all+YLD_Treat_all
```

## Years of Life Lost due to Neonatal deaths and fetal loss
```{r}
## Scenario Including foetal loss in the YLL estimates
YLL_all1<- YLL_NT_neo_death+YLL_Treat_neo_death+YLL_floss

## Scenario excluding Foetal loss in the YLL estimates
YLL_all2 <- YLL_NT_neo_death+YLL_Treat_neo_death
```

### Disability-Adjusted Life Years
```{r}
DALY1 <- YLD_all+YLL_all1
## Without foetal loss in the estimates
DALY2 <- YLD_all+YLL_all2
```

### PARAMETERS FOR COSTS-ECONOMIC BURDEN
## currency conversion factor, Burundian francs to US Dollar
```{r}
bif2usd<- 1915
```

## Epidemiological paramters for costs
```{r}
### Proportion of pregnant women visiting health care
PHC_toxo <-0.1

### Proportion of seroconverting Women taking tretament
HC_Women_treat <- 0.3

### number of visits to hospital, Uniform parameters for suspected 
n_visit_med_min <- 2
n_visit_med_max <- 4
n_visit_med <- runif(n, n_visit_med_min, n_visit_med_max)

## cost of medical Consultation, gamma parameter
Cconsult_day_shape <-3.31
Cconsult_day_rate <- 0.000661
Cconsultation <-rgamma(n, Cconsult_day_shape, Cconsult_day_rate)

## price of medication by month, Fixed
Cost_spiramycin_min<-270000
Cost_spiramycin_max <-360000
Cost_spiramycin <-runif(n, Cost_spiramycin_min, Cost_spiramycin_max)

## price of diagnostic test, Gamma distribution
Cost_diagnostic_shape<- 2.94
Cost_diagnostic_rate<- 0.000196
Cost_diagnostic<-rgamma(n, Cost_diagnostic_shape, Cost_diagnostic_rate)

### Duration of treatment (months), uniform parameters
Duration_treat_min<-2
Duration_treat_max<-6
Duration_treat <-runif(n, Duration_treat_min, Duration_treat_max)
```

### SIMULATIONS, HUMANS
```{r}
### Number of women consulting hospital for toxo (IgG+/- and IgM-) at least once
N_women_Ntoxo<-Tot_Preg*PHC_toxo

#### Women infected with toxoplasmosis visiting hospitals at least 3 times 
N_Women_PToxo <-Nseroconv*PHC_toxo

### Women positive for toxoplasmosis and treated
N_women_treated <-N_Women_PToxo*HC_Women_treat
```

### COSTS, HUMANS
##### Consultation and diagnostic
```{r}
### Cost_healthcare for women visiting hospital for toxo consultation and diagnosis
Cost_Consult1 <-N_women_Ntoxo*Cconsultation
Cost_dg1 <-N_women_Ntoxo*Cost_diagnostic
Cost_Hcare1 <-Cost_Consult1+Cost_dg1

### Costs for women infected with toxoplasmosis
Cost_Consult2<-N_Women_PToxo*n_visit_med*Cconsultation
Cost_dg2 <-N_Women_PToxo*n_visit_med*Cost_diagnostic
Cost_Hcare2<- Cost_Consult2+Cost_dg2

### Total costs for Consultation 
Cost_tot_consult <-Cost_Consult1+Cost_Consult2

### Total costs for diagnostic
Cost_tot_dg <-Cost_dg1+Cost_dg2

## Medication costs for women treated
Cost_medicine <-N_women_treated*Cost_spiramycin*Duration_treat
```

### TOTAL COSTS AND CONVERSIONS
```{r}
cost_total <-Cost_tot_consult+Cost_tot_dg+Cost_medicine
usd_cost_total <- cost_total / bif2usd
usd_Cost_tot_consultation <- Cost_tot_consult/bif2usd
usd_Cost_tot_diagnostic <-Cost_tot_dg/bif2usd
usd_cost_medicine <- Cost_medicine/bif2usd
usd_Cost_Hcare1 <-Cost_Hcare1/bif2usd
usd_Cost_Hcare2<-Cost_Hcare2/bif2usd
Usd_cost_by_NToxo<-(usd_Cost_Hcare1/(N_women_Ntoxo))
Usd_cost_by_PToxo <-((usd_Cost_Hcare2+usd_cost_medicine)/N_Women_PToxo)
Usd_cost_by_PToxo_treated <-((usd_cost_medicine+(usd_Cost_Hcare2*0.3))/N_women_treated)
usd_cost_by_PToxo_untreated <-(usd_Cost_Hcare2/N_Women_PToxo)
```

### SUMMARIES
```{r}
Summary <-
  function(x) {
    print(c(mean = mean(x),
            quantile(x, c(.025, .975))))
  }
```

## cases, deaths 
```{r}
Summary(Inc_CT)
Summary(Inc_CT_bi)
Summary(Cases_CT)
Summary(Cases_CT_NHC)
Summary(Cases_CT_treat_HC)
Summary(NT_Chorio1)
Summary(NT_Chorio2)
Summary(NT_hydrocephalus)
Summary(NT_IC_calcification)
Summary(NT_CNS_abnorm)
Summary(NT_Neon_deaths)
Summary (Nseroconv)
Summary(Nfetalloss)
```

## Treated cases
```{r}
Summary(NTreat_Chorio1)
Summary(NTreat_Chorio2)
Summary(NTreat_hydroc)
Summary(NTreat_IC_calc)
Summary(NTreat_CNS_ab)
Summary (NTreat_Neon_deaths)
```

## Total number of cases (treated + untreated)

```{r}
Summary (NT_Chorio1+NTreat_Chorio1)
Summary (NT_Chorio2+NTreat_Chorio2)
Summary (NT_hydrocephalus+NTreat_hydroc)
Summary (NT_IC_calcification+NTreat_IC_calc)
Summary (NT_CNS_abnorm+NTreat_CNS_ab)
Summary (NT_Neon_deaths+NTreat_Neon_deaths)
Summary((NT_Chorio1+NTreat_Chorio1)+(NT_Chorio2+NTreat_Chorio2)+(NT_hydrocephalus+NTreat_hydroc)+(NT_IC_calcification+NTreat_IC_calc)+(NT_CNS_abnorm+NTreat_CNS_ab))
Summary (Cases_CT-((NT_Chorio1+NTreat_Chorio1)+(NT_Chorio2+NTreat_Chorio2)+(NT_hydrocephalus+NTreat_hydroc)+(NT_IC_calcification+NTreat_IC_calc)+(NT_CNS_abnorm+NTreat_CNS_ab)+(NT_Neon_deaths+NTreat_Neon_deaths)))
```

### YLDs untreated and treated
```{r}
Summary(YLD_NT_Chorio1)
Summary (YLD_NT_Chorio2)
Summary(YLD_NT_hydrocephalus)
Summary(YLD_NT_ICC)
Summary(YLD_NT_CNS)
Summary(YLD_Treat_chorio1)
Summary(YLD_Treat_chorio2)
Summary(YLD_Treat_hydroc)
Summary(YLD_Treat_ICC)
Summary(YLD_Treat_CNS)
Summary(YLD_NT_Chorio1+YLD_Treat_chorio1)
Summary(YLD_NT_Chorio2+YLD_Treat_chorio2)
Summary(YLD_NT_hydrocephalus+YLD_Treat_hydroc)
Summary(YLD_NT_ICC+YLD_Treat_ICC)
Summary(YLD_NT_CNS+YLD_Treat_CNS)
Summary(YLD_NT_all)
Summary(YLD_Treat_all)
Summary(YLD_all)
```

## YLLs 
```{r}
Summary(YLL_floss)
Summary(YLL_NT_neo_death)
Summary(YLL_Treat_neo_death)
Summary(YLL_NT_neo_death+YLL_Treat_neo_death)
Summary(YLL_all1)
Summary(YLL_all2)
```

### DALYs
```{r}
Summary(DALY1)
Summary(DALY2)
```

### YLDs, YLLs, DALYs per 100000 population
```{r}
Summary(1e5 * YLD_all / sum(pop_mx))
Summary(1e5 * YLL_all1 / sum(pop_mx))
Summary(1e5 * YLL_all2 / sum(pop_mx))
Summary(1e5 * DALY1 / sum(pop_mx))
Summary(1e5 * DALY2 / sum(pop_mx))
```

## YLDs, YLLs, DALYs per incident case
```{r}
Summary(YLD_all / Cases_CT)
Summary(YLL_all1 / Cases_CT)
Summary(YLL_all2 / Cases_CT)
Summary(DALY1 / Cases_CT)
Summary(DALY2 / Cases_CT)
```

## YLD, YLL contribution
```{r}
Summary(YLL_all1 / DALY1)
Summary(YLL_floss/DALY1)
Summary((YLL_NT_neo_death+YLL_Treat_neo_death)/DALY1)
Summary(YLL_all2 / DALY2)
Summary(YLD_all / DALY1)
Summary((YLD_NT_Chorio1+YLD_Treat_chorio1)/DALY1)
Summary((YLD_NT_Chorio2+YLD_Treat_chorio2)/DALY1)
Summary((YLD_NT_CNS+YLD_Treat_CNS)/DALY1)
Summary((YLD_NT_hydrocephalus+YLD_Treat_hydroc)/DALY1)
Summary((YLD_NT_ICC+YLD_Treat_ICC)/DALY1)
Summary(YLD_all / DALY2)
Summary((YLD_NT_Chorio1+YLD_Treat_chorio1)/DALY2)
Summary((YLD_NT_Chorio2+YLD_Treat_chorio2)/DALY2)
Summary((YLD_NT_CNS+YLD_Treat_CNS)/DALY2)
Summary((YLD_NT_hydrocephalus+YLD_Treat_hydroc)/DALY2)
Summary((YLD_NT_ICC+YLD_Treat_ICC)/DALY2)
```

### TOTAL COSTS_TOXOPLASMOSIS
```{r}
Summary(cost_total)
Summary(usd_cost_total)
Summary(usd_Cost_tot_consultation)
Summary(usd_Cost_tot_diagnostic)
Summary(usd_cost_medicine)
Summary(Cost_tot_consult/ cost_total)
Summary(Cost_tot_dg/ cost_total)
Summary(Cost_medicine/ cost_total)
Summary(usd_Cost_Hcare1)
Summary(usd_Cost_Hcare2)
Summary(Usd_cost_by_NToxo)
Summary(Usd_cost_by_PToxo)
Summary(Usd_cost_by_PToxo_treated)
Summary(usd_cost_by_PToxo_untreated)
```

#### SENSITIVITY ANALYSES
### SENSITIVITY ANALYSIS FUNCTIONS

```{r}
## standardized regression coefficients
sa_src <-
function(y, x) {
  df <- as.data.frame(apply(x, 2, scale))
  summary(lm(scale(y) ~ ., data = df))
}

## partial correlation coefficients
sa_pcc <-
function(y, x) {
  out <- matrix(ncol = 2, nrow = ncol(x))
  colnames(out) <- c("rho", "p")
  rownames(out) <- colnames(x)

  for (i in seq(ncol(x))){
    lm_y <- lm(y ~ x[, -i])      # regress y to other x's
    lm_x <- lm(x[, i] ~ x[, -i]) # regress x to other x's
    out[i, ] <-
      unlist(cor.test(lm_y$residuals, lm_x$residuals)[4:3],
             use.names = FALSE)
  }

  return(out[order(abs(out[, "rho"]), decreasing = TRUE), ])
}
```

### TORNADO GRAPH
```{r}
## requires library ggplot2
library(ggplot2)

## ggplot2
tornado <-
function(coef, names = NULL) {
  ## copy names if needed
  if (is.null(names)) names <- rownames(coef)

  ## create data frame
  df <- data.frame(est = coef[, "rho"],
                   order = order(abs(coef[, "rho"])),
                   name = names)

  ## sort data frame
  df <- df[df$order, ]

  ## create ggplot
  ggplot(df, aes(x = order, y = est)) +
    geom_bar(stat = "identity") +
    coord_flip() +
    scale_x_continuous(element_blank(),
                       breaks = seq(nrow(df)),
                       labels = df$name) +
    scale_y_continuous("partial correlation coefficient",
                       limits = c(min(0, min(df$est) - 0.1),
                                  max(0, max(df$est) + 0.1))) +
    geom_text(aes(x = order, y = est, label = formatC(est, 3, form = "f")),
              size = 3,
              hjust = ifelse(df$est > 0, -0.1, 1.1),
              vjust = 0.4) +
    theme_bw()
}
```

#### TOTAL DALYs

```{r}
sa_src(DALY1,
       cbind(Pseroneg, Pserop, PTTMoth_fet, P_fetalloss, Chorio1, 
             Chorio2,Hydrocephalus,IC_Calcification, CNS_ab, Neon_deaths))

sa_daly1_pcc <-
  sa_pcc(DALY1,
         cbind(Pseroneg, Pserop, PTTMoth_fet, P_fetalloss, Chorio1, 
               Chorio2,Hydrocephalus,IC_Calcification, CNS_ab, Neon_deaths))
sa_daly1_pcc

## tornado graph
daly1_items <-
  c("Proportion of foetal loss","Proportion seropositive",
    "Proportion CNS","Proportion of neonatal deaths",
    "Proportion hydrocephalus","Proportion chorio 1",
    "Proportion seronegative","Proportion ICC",
    "Proportion chorio 2","Seroconversion rate")

png("sa_daly1_pcc.png",  7, 3.5, units = "in", res = 400)
tornado(sa_daly1_pcc, daly1_items)
graphics.off()
```

### DALYS without foetal loss
```{r}
sa_src(DALY2,
       cbind(Pseroneg, Pserop, Chorio1, PTTMoth_fet, 
             Chorio2,Hydrocephalus,IC_Calcification, CNS_ab, Neon_deaths))

sa_daly2_pcc <-
  sa_pcc(DALY2,
         cbind(Pseroneg, Pserop, Chorio1, PTTMoth_fet,
               Chorio2, Hydrocephalus,IC_Calcification, CNS_ab, Neon_deaths))
sa_daly2_pcc

## tornado graph
daly2_items <-
  c("Proportion seropositive","Proportion CNS","Proportion of neonatal deaths",
    "Proportion hydrocephalus","Proportion chorio 1", "Proportion ICC",
    "Proportion seronegative","Seroconversion rate", "Proportion chorio 2")
    
png("sa_daly2_pcc.png",  7, 3.5, units = "in", res = 400)
tornado(sa_daly2_pcc, daly2_items)
graphics.off()
```


#### SENSITIVITY ANALYSES_ECONOMIC LOSSES
```{r}
sa_src(usd_cost_total,
       cbind(Pserop, Pseroneg, n_visit_med, 
             Cconsultation, Cost_diagnostic, Cost_spiramycin, Duration_treat))
sa_cost_pcc <-
  sa_pcc(usd_cost_total,
         cbind(Pserop, Pseroneg, n_visit_med, 
             Cconsultation, Cost_diagnostic, Cost_spiramycin, Duration_treat))
sa_cost_pcc

## tornado graph
cost_items <-
c("Cost diagnostic", "Cost consultation", "Duration of treatment", 
  "Proportion of seropositive", "Cost medicine", "Number of hospital visits", 
  "Seroprevalence negative")

png("sa_cost_pcc.png", 7, 3.5, units = "in", res = 400)
tornado(sa_cost_pcc, cost_items)
graphics.off()
```



